\documentclass{article}

\usepackage{ulem}
\usepackage{graphicx}
\begin{document}
\title{Database Project - Part 4 Database application}
    \author{Amanda Drost, Drue Bethel, Bruce Dearing\\
    Acadia University}
\date{\today}
\maketitle
\clearpage

\begin{description}

    \item[Assumptions] \hfill 
        \begin{itemize}
            \item A book will be received and picked up from the bookstore.
            \item A book may have multiple authors, however, only one publisher.
            \item A student might make multiple separate orders of books.
            \item Data for the student table and course load are generated separately
                 and batch entered.
            \item Publisher data already generated and Publisher ID derived from ISBN.
            \item Employee data separate from simple login information is stored on 
                  separate database.
            \item The year for section is the current fall - winter period. X1 September - December current year X2 January to April Next year.
            \item Email address length will be less than 254 characters as per RFC 2821.
            \item ISBN will be ISBN-13, any ISBN-10 numbers will be converted to ISBN-13 before entry.
            \item ISBN will have dashes included on entry, 978-0-201-70279-7 vice 9780201702797.
            \item Multiple sections of the same course will require the same book.

            \item Once logged on admin users are trusted that invalid or harmful  
                data will not be entered.
        \end{itemize}
\end{description}

\end{document}
